Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-12-21 analysis/paper/paper.Rmd
Update paper and template

knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  relative_path = TRUE,
  comment = "#>",
  fig.path = "../figures/",
  dev = c("postscript"),
  fig.width = 6.85,
  fig.height = 6.85,
  out.width = "100%",
  dpi = 300
)

@@

Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15--40&nbsp;\% of irrigation water while not affecting yield [@Bouman2001; @Liping2007]. In AWD rice, fields are exposed to several dry phases during the growing season without exposing the plants to water stress. In order to avoid yield decline under AWD, "safe" thresholds have been developed. Under safe AWD irrigation water is applied when the field water level reaches 15&nbsp;cm below the soil surface [@Richards2014]. Fields are furthermore kept puddled with water standing during the flowering period to avoid plant stress. As an added benefit to saving water, AWD also reduces greenhouse gas (GHG) emissions of rice fields, which are a substantial factor in the GHG budget of rice producing countries, by around 50 &nbsp;\% [@Yan2005; @Sander2015].

>>>>

knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  relative_path = TRUE,
  comment = "#>",
  fig.path = "../figures/",
  dev = c("postscript"),
  dpi = 300
)

@@

Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15--40&nbsp;\% of irrigation water while not affecting yield [@Bouman2001; @Feng2007]. In AWD rice, fields are exposed to several dry phases during the growing season without exposing the plants to water stress. In order to avoid yield decline under AWD, "safe" thresholds have been developed. Under safe AWD irrigation water is applied when the field water level reaches 15&nbsp;cm below the soil surface [@Richards2014]. Fields are furthermore kept puddled with water standing during the flowering period to avoid plant stress. As an added benefit to saving water, AWD also reduces greenhouse gas (GHG) emissions of rice fields, which are a substantial factor in the GHG budget of rice producing countries, by around 50 &nbsp;\% [@Yan2005; @Sander2015].
